---
title: "Homework 5"
author: "Bingkun Luo"
date: "11/2/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(kableExtra)
library(readr)
library(data.table)

```

### Problem 1
```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

General glance for the data:

```{r}
str(iris_with_missing)


kable(head(iris_with_missing),format = "markdown")
```

Since there is only two cases for missing value, either numeric or character, we apply the function below and there is the table for the final result of replacing iris missing data:

```{r}
replace = function(x){
        if (class(x) == "numeric") {replace_na(x, mean(x, na.rm = TRUE))}       
        else if (class(x) == "character") {replace_na(x, "virginica")} 
                }

##apply using map

final_iris = map_df(iris_with_missing, replace)

kable(final_iris,format = "markdown",digits = 3)
```


### Problem 2

```{r}
input_files = list.files(path = './data/data', full.names = TRUE)


input_data = purrr::map_df(input_files, ~read.csv(.))

output_data = input_data%>%
       pivot_longer(week_1:week_8,
       names_to = "week",
       values_to = "data")%>%
       mutate(subject_id = c(rep("con_1",8),rep("con_2",8),
                     rep("con_3",8),rep("con_4",8),
                     rep("con_5",8),rep("con_6",8),rep("con_7",8),rep("con_8",8),
                     rep("con_9",8),rep("con_10",8),
                     rep("exp_1",8),rep("exp_2",8),rep("exp_3",8),rep("exp_4",8),
                     rep("exp_5",8),rep("exp_6",8),rep("exp_7",8),rep("exp_8",8),
                     rep("exp_9",8),rep("exp_10",8)),
              type = c(rep("control",80),rep("experiment",80)),
              type = as.factor(type))%>%
  group_by(week)

```


#### Graph
```{r}

ggplot(output_data ,aes(x = week, y = data, group = subject_id, color = type)) +
  geom_line() +
   labs(
    title = "Plot for control arm vs. experiment arm",
    x = "Observation time",
    y = "Data for arm",
    caption = "Data from zip")

```

*Comments*:

The observed data shows that the experiment arms have a overall larger number than the control group. Experiment arm data has an increasing trend over the study period, which is eight weeks, at the end of the study experiment data could be doubled. Whereas, the control group seems more flat over time and did not develop a trend.



### Problem 3

#### Step 1
```{r}

simulate_fun = function(n,beta_0,beta_1,var){
  tibble(
  x = rnorm(n),
  y = beta_0+beta_1*x+rnorm(n,mean = 0,sd = sqrt(var)))
}


set.seed(1)
data_1 = rerun(10000, simulate_fun(30,2,0,50))
linear = map(data_1,~broom::tidy(lm(y~x, data = .)))

summary_1 =  data_1%>%
             tibble(beta_1 = 0,
                    linear,
                    estimate = map(linear, ~ .x[2,2]),
                    p_value = map(linear, ~ .x[2,5]))%>% 
             unnest(estimate:p_value) %>% 
             select(-linear)
  

summary_1


kable(head(summary_1),digits = 3)

  


```
```{r}
#data_2 = append(rerun(10000, simulate_fun(30,2,1,50)),
#              rerun(10000, simulate_fun(30,2,2,50)),
#              rerun(10000, simulate_fun(30,2,3,50)),
#              rerun(10000, simulate_fun(30,2,4,50)),
#              rerun(10000, simulate_fun(30,2,5,50)),
#              rerun(10000, simulate_fun(30,2,6,50)))

#linear = map(data_2,~broom::tidy(lm(y~x, data = .)))

#summary_2 =  data_1%>%
             #tibble(linear,
                #     beta_1 = c(rep(1,10000),rep(2,10000),rep(3,10000),
                #               rep(4,10000),rep(5,10000),rep(6,10000)),
                #   estimate = map(linear, ~ .x[2,2]),
                #  p_value = map(linear, ~ .x[2,5]))%>% 
            # unnest(estimate:p_value) %>% 
            # select(-linear)
  

#summary_2
```



#### Step 2
```{r}
set.seed(1)


sim_regression = function(n, beta_0, beta_1,var,simulate_fun) {
    tibble(
      true_beta = beta_1,
      sim_data =rerun(10000, simulate_fun(30,2,beta_1,50)),
      ls_fit = map(sim_data,~broom::tidy(lm(y ~ x, data = .))),
      estimate = map(ls_fit, ~ .x[2,2]),
      p_value = map(ls_fit, ~ .x[2,5]))%>% 
  unnest(estimate:p_value) %>% 
  select(-ls_fit)
  
}
      
beta_1 = list(1,2,3,4,5,6)

sim_results = 
  map(beta_1, ~sim_regression(30,2,.x,50,simulate_fun))%>% 
  bind_rows()

  

```

#### Step 3
```{r}
beta_1_combine = list(0,1,2,3,4,5,6)

summary_final = 
  map(beta_1_combine, ~sim_regression(30,2,.x,50,simulate_fun))%>% 
  bind_rows()

```





#### Plot

```{r}
plot_1 = summary_final%>%
         group_by(true_beta)%>%
         mutate(p_reject = sum(p.value < 0.05)/length(p.value))
  
ggplot(plot_1,aes(x = true_beta, y = p_reject, col = true_beta)) +
  geom_point() +
  geom_line()+
   labs(
    title = "The power of the test",
    x = "True Beta_1",
    y = "proportion of times the null was rejected",
    caption = "Data from simulation")
  

```





```{r}
plot_2 = summary_final%>%
         group_by(true_beta)%>%
         summarize(mean_beta = mean(estimate)) 
   
  
  
ggplot(plot_2,aes(x = true_beta, y = mean_beta, col = true_beta)) +
  geom_point()+ 
  geom_line()+
  labs(
    title = "",
    x = "True Beta_1",
    y = "Average estimate of Beta_1 ",
    caption = "Data from simulation")
  

```


```{r}
plot_3 = summary_final%>%
         filter(p.value < 0.05) %>%
         group_by(true_beta)%>%
         summarize(mean_beta = mean(estimate)) 


ggplot(plot_2,aes(x = true_beta, y = mean_beta, col = true_beta)) +
  geom_point(alpha = 0.5)+ 
  geom_line(col = "sky blue")+
  geom_point(data = plot_3,alpha = 0.5)+
  geom_line(data = plot_3,col="orange")+
  labs(
    title = "",
    x = "True Beta_1",
    y = "Average estimate of Beta_1 ",
    caption = "Data from simulation")

```

